\input{macros-cs412.tex}

%\documentclass{article}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\setlength{\parindent}{0pt}
\usepackage{graphicx}
\usepackage{ctable}
%\usepackage{fullpage}
%\usepackage{setspace} 
\usepackage{float}
%\usepackage{listings} 
%\usepackage{bbm}
\usepackage{bigstrut}
%\usepackage{caption}
%\usepackage{subcaption}
%\usepackage{algpseudocode}
%\usepackage{algorithm}

\usepackage{listings}
\usepackage{color}
\usepackage[utf8]{inputenc}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=matlab,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}


\oddsidemargin 0in
\evensidemargin 0in
\textwidth 6.5in
\topmargin -0.5in
\textheight 9.0in
\usepackage{multirow}
\usepackage{hyperref}

\hypersetup{colorlinks=true}
\usepackage{color}

\newenvironment{ans}{%
	\vspace{5mm}
	\textcolor{red}{{\sf Answer}}\\%
}
{%
}

\begin{document}


\solution{}{Due: 12/1/2015 11:59pm}{Assignment 5}{Fall 2015}
% Fill in the above, for example, as follows:
% \solution{Joe Smith}{\today}{1}{Fall 2012}

\pagestyle{myheadings}  % Leave this command alone

\paragraph*{General Instruction}
\begin{itemize}\vspace{-2mm}\setlength\itemsep{0mm}
	\item Errata: After the assignment is released, any further corrections of errors or clarifications will be posted at \href{https://piazza.com/class/idqujg4tiae3q0?cid=93}{the Errata page at Piazza}. Please watch it.
	\item Feel free to talk to other members of the class while doing the homework. We are more concerned that
	you learn how to solve the problem than that you solve it entirely on your own. You should, however, write the solution yourself. 
	\item Please use Piazza first if you have questions about the homework. Also feel free to send us e-mails and come to office hours. 
	\item For each question, you should show the necessary calculation steps and reasoning---not only final results. Keep the solution brief and clear.
	\item For a good balance of cognitive activities, we label each question with an activity type:
	\begin{itemize}
		\item {\bf L1 (Knowledge)} Definitions, propositions, basic concepts.
		\item {\bf L2 (Practice)} Repeating and practicing algorithms/procedures.
		\item {\bf L3 (Application)} Critical thinking to apply, analyze, and assess.
	\end{itemize}
\end{itemize}
\paragraph*{Assignment Submission}
\begin{itemize}\vspace{-2mm}\setlength\itemsep{0mm}
	\setlength{\itemsep}{2pt}
	\item Please submit your work before the due time. \textbf{We do NOT accept late submission!}
	\item 
	Please submit your answers electronically via  \href{http://compass2g.illinois.edu}{Compass}. Contact CITES/TAs if you have technical difficulties in submitting the assignment.
	\item Please {\bf type} your answers in an \textbf{Answer Document}, and submit it in PDF. \textbf{Handwritten answers or hand-drawn pictures} \textbf{are not acceptable}. Your answers to all questions (including mini-MP) should be included in one Answer Document.
	\item Please \textbf{DO NOT} zip the Answer Document (PDF) so that the graders can read it directly on Compass.  
	Compress other files into a single zip file. Overall, you need to submit one Answer Document (PDF file), named as \texttt{hw5\_netid.pdf}, and one \texttt{zip} file, named as \texttt{hw5\_netid.zip}.
	\item If scripts are used, you should submit the source code, and use file names to identify the questions or sub-questions being answered. E.g., \texttt{question1\_netid.py} is the python code for Question 1; and \texttt{question1a\_netid.py} that for sub-question 1(a). You can submit separate files for sub-questions or a single file for the entire question. 
\end{itemize}
\input{conceptual_questions}
\input{jia}
\input{long}
\end{document}